\section{Conclusion}
\label{sec:conclusion}

%This report's aim was to showcase the final design that was preferred over other choices in the Conceptual Design Report. All modules were thoroughly explained and backed up with related test results.

%With this report, Felerest shows that it is capable of taking this project to the next level and mass produce autonomous cat feeding systems. All sub-modules are up to par and ready to be a part of the end result. This is demonstrated by test results and relevant pictures.

Looking at the environment one can see the food leftovers that cause visual pollution which also leads to health and hygiene problems. Felerest are determined to solve these problems while protecting our beloved friends. To do so, Felerest engineers are determined to create novel ideas which will lead the field of automatic cat feeding systems. Our goal is to improve the life standard of the cats and humans by using the blessings of technology. 

This report's aim was to showcase the final design that was preferred over other choices in the Conceptual Design Report. All modules were thoroughly explained and backed up with related test results.

The purpose of this project is not to only feed cats, but also to start a new product that considers cat needs. Felerest also offer features for extensive cat feeding such that it respects the cats for the required amount of food while also determining their eating behaviours, without any human interaction. This project is useful for the owners which can not leave home due to their cats and for those cats who lives in the streets or in sanctuaries who are in need of human care. Happiness and healthy care of cats to get customer satisfaction is the main purpose of Felerest team.
 % bıraya alalım mı 
  %Bence de ya<
Every module's test results, planned future test ideas, the foreseen risks and disadvantages were discussed thoroughly. Furthermore, each engineer's following responsibilities and the role division was separated reasonably. This report includes flow charts that explain the algorithms implemented in the computer vision part, 3D designs of the mechanical structures, pictures of test results for each subsystem, compatibility analysis of overall system, expected power consumption, and cost analysis. This report was written in order to show a clear picture of the project for customers and members of the company. We believe that customers should always have the chance to personalize their products. This is why Felerest provides customer oriented additional features to the mobile/web applications. 

With this report, Felerest team shows that it is capable of taking this project to the next level and mass produce autonomous cat feeding systems. All sub-modules are up to par and ready to be a part of the end result. This is demonstrated by test results and relevant pictures.

Our vision for the future is to market these feeding systems commercially available to everyone around the world. This way our furry little companions are never hungry and are always well taken care of. This will surely be an important step for the pet society, making it the first ever connected, smart, cat feeder. 