% TODO - Ilk paragraf baglanacak 

\section{Introduction} \label{sec:intro}

% Think about a cat alone in darkness with a hungry stomach waiting for her owner.

Are cats only a means to joy for humans, or are they rather precious companions? It is easier to answer this question after a quick reminder of a historical event: In \(14^{th}\) century, Europe was swept over by a plague, mainly resulted by the bites of infected rats, lice and mice. People of Europe at the time were certain that this plague was God's punishment, so the `logical' reaction was to execute Jews and alleged witches. During this manhunt, some communities also massacred village cats, thinking they were associated with witches. The removal of cats from the equation allowed a crazy amount of infected rats to continue spreading the disease, which gave way to the infamous black death.

% TODO - tamamlanmalı





The current autonomous cat feeding systems have only a few capabilities and are quite costly. The state of the art, according to an article on most rated automatic cat feeding systems of 2019 \cite{cite:SOTA}, has several key features. These are large food storage capacity, portion control settings, kibble size options and pet-proofing. This system costs 150 dollars. However, we intend to achieve all of this with extra capabilities with a maximum budget of 200 dollars. The proposed system will identify and recognize different cats and track their dietary diaries. In addition to this, the proportions will be distributed regarding their adiposity. The system will be capable of feeding a large number of cats making it adoptable for usage in campuses and homes with populous cats numbers. 

