\section{Requirement Analysis} \label{sec:req_anal}

% iyisiiin 
% :DD
% 

Objectives of the project are feeding only cats, identifying new cats and recognizing them later, deterring dogs from the area, being rechargeable and portable. Also, feeding regime of identified cats are logged by the system.
The status of the food supply and battery, profiles of the cats and feeding logs will be observed in a mobile application.

Requirements of the project:
\begin{itemize}
\item The rechargeable battery is non-removable. The lithium-ion batteries are placed on battery compartment that has power input. The battery will be completely charged in 3 hours.
\item Battery lasts at least five hours. The equipment will run on 18650 Lithium-ion batteries.
\item No attachments to the animals. The animals will be identified in 4 seconds and their feeds will be automatically delivered. 
\item System should be lightweight in order to be carried by a single person. The system will be around 7 kilograms when the reservoir is full. %burdan öncekiler projede verilen requirementlar, alttakiler objective olabilir.
\item To avoid food waste, three or five times of meal will be given to a single cat in a day.
\item The dogs will be deterred with high frequency sounds in order not to damage them. The frequency will be around 30 kHz. However, high frequency sounds also affect cats. We are working for better solutions.
\item Capacity of the reservoir will be 4 kilograms which is around 45 meals.
\item Power usage should be minimized. Low current driven motor will be used.
\item Light bulb will be used at nights. When the motion sensor is activated the bulb will turn on and it will turn off in 2 minutes. By this way, redundant use of electricity will be eliminated.
\item The identification process should be fast. It will last 4 seconds, after cat enters the area. % 3.maddeye benzer oldu
\end{itemize}