\section{Solution Procedure} \label{sec:sol_proc}

% TODO: TAM OLARAK YAPILMASI GEREKENLERİ YAZMADIM AMA ÇOĞUNU YAZDIM. YAZILMASI GEREKEN ŞEYLER: 
% 1: DURATİON YAZILMALI.
% 2: SEQUENCE GÖSTERİLMELİ. 
% TÜM BUNLARI GANTCHART DA GÖSTEREBİLİRİZ DİYE DÜŞÜNDÜM O YÜZDEN YAZMADIM. 
% 3: COMPUTER VİSİON KISMI YAZILMALI.

Different approaches can be applied in order to meet the specifications. As Felerest, our goal is to determine the best solution in order to solve the problems which will be mentioned in this section. 

There exist several problems like:

1. Determining the cats and dogs from other animals.

2. Categorizing the cats and determining their behaviours. 

3. Giving the right amount of food and water.

4. The amount of food and water left should be shown.

5. Non stop working for X hours.

6. Controlling the electronic devices in order to protect the device from over voltage and heat. 

As mentioned in the above section our system should detect and differ cats from dogs. Moreover cats must be categorized and must be given the sufficient amount of food, not more not less. Dogs must escape from the area. In order to honor the specifications, after a lot of research and hard work, innovator designs and effective solutions are planned.

Biggest problem that can cause trouble is determining the cats and categorizing them. The solution for this problem can be found by looking for open source codes which are already working. By this way one can solve the future problems that might arise by writing the code from scratch and moreover, by adding necessary parts, detecting our little friends is no longer a problem. 

Mechanical part should be designed, such that system should adjust the necessary amount of food. This can be done by controlling the flow of the food via door. This door must cut the food flow by the command coming from the controller. Therefore it must be a hard solid material that can move easily or rotate by a simple low power motor like a cheap servo\cite{cite:cheapservo}. Low power motor is important since it is cheaper and consumes less energy which is important for satisfying the \(5^{th}\) condition. The amount of food and water should be checked by a sensor like sonar or weight sensor. 

Electronics part should be designed such that it must consume low power and should resist the overheat. Catching high resolution photographs is a necessity for face recognition part. Moreover in order to meet specifications, the system should deter the dogs without give any harm. This problem can be solved by disturbing the dogs by using a high frequency signal\cite{cite:Dogrepellingdetterent} or using a harmless sprey\cite{cite:Dogrepellingsprey}  that dogs are sensitive.

The planned schedule can be seen below as a Gantt Chart.
 
\subsection{Computer Vision} \label{sec:sol_proc} % instead of '5.1', just 'a'
 
\subsection{Mechanical Design} \label{sec:sol_proc} % instead of '5.1', just 'a'
\begin{itemize}
\item Immediate response from controller. 

\item Controlling the food flow effectively.

\item Adding sensors which will measure the amount of food and water.

\item Consumption of less power. 
\end{itemize}

\subsection{Electronics Design} \label{sec:sol_proc} % instead of '5.1', just 'a'

\begin{itemize}
\item Consuming low power.

\item Resistant to heat power. 

\item Controlling mechanism to detect overheating or overvoltage. 

\item Deterring the dogs without giving any harm.

\end{itemize}
