\section{Solution Approach} \label{sec:sol_appr}

% TODO: TAM OLARAK YAPILMASI GEREKENLERİ YAZMADIM AMA ÇOĞUNU YAZDIM. YAZILMASI GEREKEN ŞEYLER: 
% 1: DURATİON YAZILMALI.
% 2: SEQUENCE GÖSTERİLMELİ. 
% TÜM BUNLARI GANTCHART DA GÖSTEREBİLİRİZ DİYE DÜŞÜNDÜM O YÜZDEN YAZMADIM. 
% 3: COMPUTER VİSİON KISMI YAZILMALI.
\input{content/solutionApproachV3.tex}
Below you can see the detailed working areas for four groups and planned schedule can be seen as a Gantt Chart.
 
\subsection{Mechanical Design} \label{sec:sol_proc} % instead of '5.1', just 'a'
\begin{itemize}
\item Immediate response from controller. 

\item Controlling the food flow effectively.

\item Integration of food mechanism.

\item Making realistic tests.

\item Consumption of less power. 
\end{itemize}

\subsection{Electronics Design} \label{sec:sol_proc} % instead of '5.1', just 'a'

\begin{itemize}
\item Deterring the dogs without giving any harm. 

\item Selecting the right sensor, microprocessor and regulator.

\item Calculating the overall power of the system and selecting the right battery. 

\item Generating a good control mechanism for the overheating and overvoltage.

\item Making real time tests.

\end{itemize}

\subsection{Computer Vision} \label{sec:sol_proc} % instead of '5.1', just 'a'
\begin{itemize}
\item Making a search for features of the cats and dogs.

\item Searching for open source codes. 

\item Improving and implementing codes. 

\item Testing and concluding the CV part.  

\end{itemize}
\subsection{Back-end software Framework} \label{sec:sol_proc} % instead of '5.1', just 'a'
\begin{itemize}
\item Transferring video data. 

\item Establishing the communication between microprocessors and server.

\item Designing the interface for computer camera and website.

\item Building a user friendly website.

\item Testing and concluding.
\end{itemize}
%Computer vision part is responsible for detecting the cats and classify them. In addition to that dogs must be detected as a thread. Since all animals have their characteristic shapes depending on their species, one can use this animal specific details in order to categorize and differ animals. There exist several open source codes which can be used freely. By looking for these codes and improving the necessary parts, detecting our little friends will no longer be a problem.

%Back-end part is responsible for the software part of the project. There will be several problems after and before the detecting animals like transferring video data, communication between microprocessors and server. Moreover in order to be a user friendly, Felerest will develop a website which, user can check the critical informations like voltage and food level. All of this parts requires a good computer knowledge which our team is very capable of doing that. Firstly a good literature search will be done in order to gain the vision to solve these problem. After that, application of this ideas to our project will be done. Testing these solutions with a real world examples, we will conculude also this part.

