
There exist several problems such as:

1. Determining the cats and dogs from other animals.

2. Categorizing the cats and determining their behaviours. 

3. Giving the right amount of food and water.

4. The amount of food and water left should be shown.

5. Non stop working for 5 hours.

6. Controlling the electronic devices in order to protect the device from over voltage and heat. 

As mentioned in the above section our system should detect and differ cats from dogs. Moreover cats must be categorized and must be given the sufficient amount of food, not more not less. Dogs must escape from the area. In order to honor the specifications, after a lot of research and hard work, innovator designs and effective solutions will be planned.

Mechanical part should be designed, such that system should adjust the necessary amount of food. This can be done by controlling the flow of the food via door. This door must cut the food flow by the command coming from the controller. Therefore it must be a hard solid material that can move easily or rotate by a simple low power motor like a cheap servo\cite{cite:cheapservo}. Low power motor is important since it is cheaper and consumes less energy which is important for satisfying the \(5^{th}\) condition. After deciding the gate type, food mechanism should be integrated to the gate. These two parts should be perfectly matched since controlling the flow of the food is critical for this project. In every sub-step of this mechanical part, tests will be done with a thinking about every detail. Real time examples will be tested on every sub-step.  

Electronics part should be designed such that it must consume low power and should be effective to make critical jobs. This part consists of four different task like: Dog deterring system, design of power electronics, sensor and microprocessor selection and integration, battery selection and placement. Every sub-part is critical since they all contribute to the other parts of the project. The system should deter the dogs without give any harm. This problem can be solved by disturbing the dogs by using a high frequency signal \cite{cite:Dogrepellingdetterent} or using a harmless spray \cite{cite:Dogrepellingsprey}  that dogs are sensitive. For both of the solutions a controller should be designed such that when there is a threat, the deterring system should be trigger. Since our electronic devices will only work at certain voltage levels, regulators will be needed. After the selection of the electronic devices right regulators will be selected and will be checked if the system runs as expected.  The amount of food and water should be checked by a sensor like sonar or weight sensor. This sensor should be selected such that it should work with a good precision since our controller will depend on that. In order to select the right sensor a web research will be conducted and after selecting the sensor, the necessary test will be done on it until requirements are fulfilled.
Moreover since our design will work for five hours, a battery must be selected according to the power consumption of the circuit. By simulating the power consumption, effective battery will be selected.

Back-end part is responsible for the software part of the project. There will be several problems after and before the detecting animals like transferring video data, communication between microprocessors and server. Moreover in order to be a user friendly, Felerest will develop a website which, user can check the critical informations like voltage and food level. All of this parts requires a good computer knowledge which our team is very capable of doing that. Firstly a good literature search will be done in order to gain the vision to solve these problem. After that, application of this ideas to our project will be done. Testing these solutions with a real world examples, we will conclude also this part.

Computer vision part is responsible for detecting the cats and classify them. In addition to that dogs must be detected as a threat. Since all animals have their characteristic shapes depending on their species, one can use this animal specific details in order to categorize and differ animals. There exist several open source codes which can be used freely. By looking for these codes and improving the necessary parts, detecting our little friends will no longer be a problem.
