% Bu sonradan yazilan, implementasyon detayına inmeyen kısım

As Felerest our goal is to make life easier for you and our little friends, therefore, we have developed innovative solutions. 

There might exist some problems in the user's mind like the weight of the total system, the capability for recognising cats and cataloging them, the warning system for the low food and water amount or due to the danger from the dog and if there exist an application which you can check them. 

Our engineers are sure that they can manage the weight problem. First results shows that the average weight will be around 4 kg approximately, which is suitable for a human to lift it. The weight mainly due to the mass of the food, electronic devices and mechanical parts. The mechanical team is determined to lower the mass, and research about the economical and sturdy materials are going on. This research will be conducted on both practical and theoretical way. Mechanical team will refer to the both the workers working at industrial area and the web. Moreover by adding a wheel one can easily pull the system without harming it.

Computer vision part is responsible for detecting the cats and classify them. In addition to that dogs must be detected as a threat. Since all animals have their characteristic shapes depending on their species, one can use this animal specific details in order to categorize and differ animals. There exist several open source codes which can be used freely. By looking for these codes and improving the necessary parts, detecting our little friends will no longer be a problem.

A warning system will be implemented in order to deter the dogs. This deterring will be harmless. In order to achieve that, there will be a web research to determine the things that dogs do not like. First observations shows that using a high frequency signal\cite{cite:Dogrepellingdetterent} or a harmless spray\cite{cite:Dogrepellingsprey} can fix the problem. 

Back-end software group also working on a software program that you can check the amount of the food and water by looking your phone. Moreover, this program will also show the voltage level and will warn you when battery is low. In order to develop the software program a good literature search will be conducted 

The project can be divided into four subgroups in order to solve the problems. These subgroups can be seen at team organization part. Different approaches can be applied in order to meet the specifications. As Felerest, our goal is to determine the best solution in order to solve the problems.
