\section{Introduction}
\label{sec:introduction}


On the challenging path of forming a novel engineering application, the Felerest team has come closer to achieving the final version of the Smart Connected Cat Feeding \& Monitoring System. This report examines each system, sub-systems and the components forming these sub-systems with a top to down structure. In the end the reader will have knowledge about: test results of these parts and their performances, what the final version will be, any changes in the design and its reasoning. The mentioned parts will be indicated through flow charts, block diagrams, and 3D drawings where applicable. The examination of each part will be done in detail mentioning technical details, work principles, proof that requirements are satisfied, discussions on compatibility, design reasoning, any trade-offs and their justifications, problems encountered and how our exceptional team of engineers have overcome it. These sum up the theoretical backbone of the project, how this knowledge has been put into application and problems faced in implementation, the unique and creative solutions overcoming these problems will additionally be present in this report. 

For the report to be comprehensive to the reader the report will be in top-down structure as mentioned. To assure this, an overall view of the system will be given as a starter. This will then be followed with sub-system explanations. The aforementioned details given will be inclusive for both the overall and sub-system explanations. Within these sub-system explanations each component forming it will also be explained in detail. In the latter parts, a general compatibility and cost analysis will be done. In this compatibility analysis the reader will be introduced to the signal interfaces and their descriptions. The server-client model can also be included as a part of this interface although it is mentioned as a sub-system under the caption 'System Architecture'. The cost analysis will be broken down in detail with explanations. The final element of the report will be to discuss the power distribution in the overall system. The calculations done in power usage will be a proof of the satisfaction of a specific requirement which is the battery usage of at least 5 hours. Our highly talented team has exceeded this limit to provide our customers for a longer duration of functioning. Last but not least, the recent and updated Gantt Chart will be provided in the Appendix section. 

To sum, this report concludes the possible design ideas presented in the previous report (Conceptual Design Report). The reader will be confident why the final design was preferred over other choices, why adjustments have been made if there are any and will have an intuition of how the project will function and look like in the end. Since the current status of the project is almost ready for mass production, the visualization of many sub-systems and the overall design (outer shell) of the system is ready for view and will be supported with photos throughout this report. 
